`mathml`: Translate R Expressions to MathML and LaTeX

### 2023-04-07 rj/mathml.Rmd
\ removed

```{r mistakes, echo=FALSE}
op1 <- list(
  "omit_left(a\\ +\\ b)"=quote(omit_left(a + b)),
  "omit_right(a\\ +\\ b)"=quote(omit_right(a + b)),
  "list(quote(a),\\ quote(omit(b)))"=list(quote(a), quote(omit(b))),
  "add_left(a\\ +\\ b)"=quote(add_left(a + b)),
  "add_right(a\\ +\\ b)"=quote(add_right(a + b)),
  "list(quote(a),\\ quote(add(b)))"=list(quote(a), quote(add(b))),
  "instead(a,\\ b)\\ +\\ c"=quote(instead(a, b) + c))

>>>>

```{r mistakes, echo=FALSE}
op1 <- list(
  "omit_left(a+b)"=quote(omit_left(a + b)),
  "omit_right(a+b)"=quote(omit_right(a + b)),
  "list(quote(a),quote(omit(b)))"=list(quote(a), quote(omit(b))),
  "add_left(a+b)"=quote(add_left(a + b)),
  "add_right(a+b)"=quote(add_right(a + b)),
  "list(quote(a),quote(add(b)))"=list(quote(a), quote(add(b))),
  "instead(a,b)+c"=quote(instead(a, b) + c))
